MAESTROeX

### 2018-12-19 MAESTROeX_I/paper.tex
add refs, some intro

\title{Title}

@@

\correspondingauthor{Doreen Fan}
\email{DFan@lbl.gov}

@@

%% Mark off the abstract in the ``abstract'' environment.
\begin{abstract}
Insert abstract here.

@@

The key numerical developments of the MAESTRO algorithm are presented in a series of papers which we refer to as papers I-V (\cite{MAESTRO_I,MAESTRO_II,MAESTRO_III,MAESTRO_IV,MAESTRO_V}, respectively).

%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

>>>>

\title{MAESTROeX}

@@

\correspondingauthor{MAESTROeX}
\email{DFan@lbl.gov}

@@

%% Mark off the abstract in the ``abstract'' environment.
\begin{abstract}
We present MAESTROeX, a next-generation solver for low Mach number astrophysical flows.
Here we summarize implementation details as well new spatiotemporal integration schemes
developed for increased accuracy and a simpler base state treatment.  The code is written
in the AMReX software framework for massively parallel block-structured adaptive mesh
refinement applications.

@@

Many astrophysical flows are highly subsonic; sound waves carry sufficiently little energy that they do not significantly affect the convective dynamics of the system.
In many of these flows, long-time convective dynamics are of interest.
Thus, using a traditional compressible astrophysical solver is highly inefficient.
One approach to this problem is to use low Mach number hydrodynamic models.

The key numerical developments of the MAESTRO algorithm are presented in a series of papers which we refer to as papers I-V (\cite{MAESTRO_I,MAESTRO_II,MAESTRO_III,MAESTRO_IV,MAESTRO_V}, respectively).
Applications include the convective phase preceding Chandrasekhar mass models for type Ia supernovae \cite{MAESTRO_convection,MAESTRO_AMR,MAESTRO_CASTRO}, 
convection in massivve stars \cite{Gilet:2013},
sub-Chandrasekhar white dwarfs \cite{subChandra_I,subChandra_II}, and
Type I X-ray bursts \cite{XRB_I,XRB_II,XRB_III}.
